Efficient modeling of timeouts in PRISM \\

### 2018-06-26 Report/tool_paper.tex
modification on the repport : removing litteral labelling in bibliography and change the title style

\title{
	%\vspace{-1in} 	
	\usefont{OT1}{bch}{b}{n}
	\normalfont \normalsize \textsc{School of random department names} \\ [25pt]
	\horrule{0.5pt} \\[0.4cm]
	\huge Efficient modeling of timeouts in PRISM \\
	\horrule{2pt} \\[0.5cm]
}
\author{
	\normalfont 								\normalsize
	Thomas Mari, M\'{a}rio Uhr\'{i}k\\[-3pt]		\normalsize
	\today
}
\date{}

@@

\usepackage[
backend=biber,
style=alphabetic,
citestyle=numeric,
sorting=none,
%sortcae=false                  
%citestyle=authoryear
]{biblatex}

@@

	\begin{abstract}
		Phase-type fitting remains the only way of modeling non-Markovian distributions within PRISM model checker.
		When analyzing models with phase-type distributions, it is problematic to obtain results of sufficient precision within reasonable time.
		We ran experimental computations and deduced a reasonable way of obtaining precise analysis results for phase-type fitted PRISM CTMCs.
		Lastly, we hint at an entirely different (and arguably better) approach to handling non-Markovian distributions.
	\end{abstract}

>>>>

\title{
	%\vspace{-1in} 	
	%\usefont{OT1}{bch}{b}{n}
	%\normalfont \normalsize \textsc{School name, institutions,...} \\ [25pt]
	%\horrule{0.5pt} \\[0.4cm]
	%\huge Efficient modeling of timeouts in PRISM \\
	Efficient modeling of timeouts in PRISM \\
	%\horrule{2pt} \\[0.5cm]
}
\author{
	\normalfont 								\normalsize
	Thomas Mari, M\'{a}rio Uhr\'{i}k\\[-3pt]		\normalsize
	\today
}
\date{}

@@

\usepackage[
backend=biber,
%this is the label style in the bibliography at the end of document
style=numeric,
%this is the label style for each citation in the document
citestyle=numeric,
sorting=none,
%sortcae=false                  
%citestyle=authoryear
]{biblatex}

@@

	\begin{abstract}
		Phase-type fitting remains the only way of modeling non-Markovian distributions within PRISM model checker.
		When analyzing models with phase-type distributions, it is problematic to obtain results of sufficient precision within reasonable time.
		We ran experimental computations and deduced a reliable way of obtaining precise analysis results for phase-type fitted PRISM CTMCs.
		Lastly, we hint at an entirely different (and arguably better) approach to handling non-Markovian distributions.
	\end{abstract}
